Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2015-05-12 version1.0/HBM.tex
adding words
testing sampling

@@

>>>>

\subsection{Calibration Data}

For our calibration of \rhostar-$F_8$, we used a sample of Kepler stars with
both asteroseismic and flicker measurements available. \citet{chaplin:2014}
report asteroseismic \rhostar\ estimates (and the associated uncertainties) for 
518 Kepler stars. The authors report three different sets of results, depending 
on the choice of \Teff\ and \FeH, and in this work we elected to use values 
reported in their Table 6 over Table 5, and Table 5 over Table 4. We 
additionally used the 71 additional planet hosting stars with asteroseismology 
reported in \citet{huber:2013} but not reported in \citet{chaplin:2014}. Values 
for flicker and range were taken from \citet{kipping:2014}, based upon the 
methods described in \citet{bastien:2013}. Following \citet{kipping:2014} and 
for reasons described there-in, we only include targets in our calibration for 
which:

\begin{itemize}
\item[{\tiny$\blacksquare$}] Range (defined in \citealt{bastien:2013}) 
$<1$\,ppt
\item[{\tiny$\blacksquare$}] $4500<T_{\mathrm{eff}}<6500$\,K
\item[{\tiny$\blacksquare$}] $K_P<14$
\item[{\tiny$\blacksquare$}] $1.2 < \log_{10}$($F_8$\,[ppm])$< 2.2$
\end{itemize}

We use the same sample for our calibration of \logg, except that we exclude the
\citet{huber:2013} data, since these authors do not provide estimates of
\logg\footnote{Whilst we could compute \logg\ ourselves from the reported
masses and radii, this could only be done under the incorrect assumption of
zero covariance between $M_{\star}$ and $R_{\star}$.}

\subsection{Hierarchical Bayesian Model}

@@

%%% logg plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{../figs/logg_vs_flicker.pdf}
\caption{
TBD
} 
\label{fig:logg}
\end{center}
\end{figure}

### 2015-05-12 version1.0/manuscript.tex
testing sampling

Whether one calibrates flicker to \logg\ or \rhostar, there are several aspects
of the problem which are attractive for our purposes of a simple demonstration
of probabilistic inference of stellar parameters. Firstly, in log-log space the
relationship is very simple, appearing to be linear. Secondly, there is a
sufficiently number of points in the sample (439 stars) to constrain a 
population-based model. Thirdly, there is significant excess scatter around the
best-fitting relation implying that a deterministic model is inadequate. For
these reasons, we identify the calibration of flicker to \logg\ and \rhostar\
as a well-posed problem to first demonstrate probabilistic inference in the 
arena of stellar characterization.

\section{HIERARCHICAL BAYESIAN MODEL}
\label{sec:HBM}

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien, 
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014} 
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781, 
124
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014} 
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015} 
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted 
(astro-ph:1504.07557)
\end{thebibliography}

>>>>

Whether one calibrates flicker to \logg\ or \rhostar, there are several aspects
of the problem which are attractive for our purposes of a simple demonstration
of probabilistic inference of stellar parameters. Firstly, in log-log space the
relationship is very simple, appearing to be linear. Secondly, there is a
sufficiently number of points in the sample (439 stars) to constrain a 
population-based model. Thirdly, there is significant excess scatter around the
best-fitting relation implying that a deterministic model is inadequate. This is
not surprising given that granulation is a complex and messy process for which
one should not expect any parametric model to provide a perfect description. For
these reasons, we identify the calibration of flicker to \logg\ and \rhostar\
as a well-posed problem to first demonstrate probabilistic inference in the 
arena of stellar characterization.

\section{PROBABILISTIC CALIBRATION}
\label{sec:HBM}

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien, 
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014} 
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014} 
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781, 
124
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013} 
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014} 
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015} 
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted 
(astro-ph:1504.07557)
\end{thebibliography}
